---
title: Extract participant data
author: "Bari Fuchs" 
output: word_document
editor_options: 
  chunk_output_type: console
---

This script was written by Bari Fuchs to compile participant data (not including decision-making variables) used in the paper 
"Decision-making processes related to perseveration are indirectly associated with weight status in children through laboratory assessed energy intake". Data for this study were drawn from a larger, cross-sectional study on the associations between decision-making, eating behavior, and weight status in children (NCT02855398). 

The output of this script will be HDT_participant_data.csv that can be combined with decision-making dataframes in 3-HDT_compile-databases.Rmd.

No variables will be computed in this script, only extracted from Shana Adise's larger study datasets.

#Isolate variables
```{r Import variables from Shana's HDT_SPSS_dataset, echo = TRUE}
library(plyr)
library(dplyr)

# set basedir to navigate to HDT directory (modify if on different machine)
basedir <- ("~/OneDrive - The Pennsylvania State University/b-childfoodlab_Shared/Inactive_Studies/DMK_Study/AB_reprocess/HDT/")

# set directory for Shana's datasets
setwd(file.path(basedir,"Spreadsheets/ShanaSpreadsheet_NOTREPROCESSED"))

# Read in Shana's datasets
Shana <-  read.csv("HDT_SPSS_database_10blocks_2_23_2017_CLB.csv", stringsAsFactors = FALSE)
Shana2 <-  read.csv("DMK_main_updated_8_18_2020_BF_transpose.csv", stringsAsFactors = FALSE)

# change ID variable name to subjID
names(Shana)[names(Shana)=="ID"] <- "subjID"
names(Shana2)[names(Shana2)=="ID"] <- "subjID"

#Extract subj ID, height, weight, BMI variables from Shana
Shana_less <- Shana[,c(1,25:32)] #subj ID, height, weight, BMI variables

#Extract demographics, sex, parents, EAH variables from Shana2
Shana2_less <- Shana2[,c(1,4:7,11,12,28,32,36,40,83:84,112:116,224,228,275:278,461:467,575:578)] 
Shana2_less$subjID <- as.numeric(Shana2_less$subjID)

# Extract liking variables
liking <- select(Shana2, starts_with("VB_Like"),starts_with("VC_Like"))
liking$subjID <- as.numeric(Shana2_less$subjID)
```

```{r Make new dataframe, echo = TRUE}

HDT_temp <- merge(Shana_less, Shana2_less, by="subjID")
HDT_participant_data <- merge(HDT_temp, liking, by="subjID")
```


# Export file
```{r Export, echo = TRUE}

# Set directory to export file to
setwd(file.path(basedir,"HDT-intake-git/Data/GeneratedDatabases"))

# write file
write.csv(HDT_participant_data,'HDT_participant_data.csv')


```


